\section{Referencias}

\begin{itemize}
	\item D'Alessio, S. (2023). Solutions of the Van der Pol Equation.\ \textit{The College Mathematics Journal}. 54:2, 90–98.\ \url{https://doi.org/10.1080/07468342.2023.2191376}
	\item Flannery, B. P., Press, W. H., Teukolsky, S. A., \& Vetterling, W. T. (2007).\ \textit{Numerical Recipes. The Art of Scientific Computing} (3ra edición). Cambridge University Press.
	\item Kanamaru, T. (2007).\ \textit{Van der Pol Oscillator}. Scholarpedia.\ \url{http://scholarpedia.org/article/Van_der_Pol_oscillator}
	\item Krantz, S. G. (2020).\ \textit{Differential Equations. A Modern Approach with Wavelets}. CRC Press.
	\item McMullen, N. (2016, diciembre 6).\ \textit{Van der Pol Equation: Overview, Derivation, and Examination of Solutions}. Nick McMullen.\ \url{https://nickmcmullen.github.io/m312_project_handout.pdf}
	\item \textit{Méthodes de Runge-Kutta}. (2020, enero). Femto.\ \url{https://femto-physique.fr/analyse-numerique/runge-kutta.php}
	\item \textit{Méthodes Numériques. Méthodes d'Euler de de Runge-Kutta d'ordre 4 pour des équations du premier ordre ou du deuxième}. (s. f.).\ Physagreg. \url{https://www.physagreg.fr/methodes-numeriques/methodes-numeriques-euler-runge-kutta.pdf}
	\item \textit{Runge Kutta Method}. (s. f.).\ StudySmarter. \url{https://www.studysmarter.co.uk/explanations/engineering/engineering-mathematics/runge-kutta-method}
	\item Tsatos, M. (2006, julio).\ \textit{Theoretical and Numerical Study of the Van der Pol Equation}. arXiv.\ \url{https://doi.org/10.48550/arXiv.0803.1658}
	\item \textit{Van der Pol Equation}. (2022, mayo 13). Encyclopedia of Mathematics.\ \url{https://encyclopediaofmath.org/index.php?title=Van_der_Pol_equation}
	\item \textit{Van der Pol Oscillator}. (s. f.).\ Department of Physics, University of Connecticut.\ \url{https://www.phys.uconn.edu/~rozman/Courses/P2200_13F/downloads/vanderpol/vanderpol-oscillator-draft.pdf}.
	\item Weisstein, E. W. (s. f.).\ \textit{Van der Pol Equation}. Wolfram MathWorld.\ \url{https://mathworld.wolfram.com/vanderPolEquation.html}
	\item Zeltkevic, M. (1998, abril 15).\ \textit{Runge-Kutta Methods}. Massachusetts Institute of Technology.\ \url{https://web.mit.edu/10.001/Web/Course_Notes/Differential_Equations_Notes/node5.html}
\end{itemize}
